Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-02 Multiresolution_framework/ltx/manuscript.tex
changed the title
cited Mallat paper

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Multi-Resolution Neural Field Estimation }

@@

The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$. Considering a one-dimensional field, the connectivity kernel is decomposed as,

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model}

@@

The multi-resolution approximation \cite{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$. Considering a one-dimensional field, the connectivity kernel is decomposed as,
